---
title: "Homicide in Toronto"
author: "Rachel Hyunbin Oh"
date: 2020-09-24T21:13:14-05:00
abstract: "Four sentences"
bibliography: "references.bib"
categories: ["R"]
tags: ["R Markdown", "plot", "regression"]
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#install.packages("tidyverse")
#install.packages("devtools")
#install.packages("ggplot2")
#devtools::install_github("sharlagelfand/opendatatoronto")
#install.packages("skimr")
#install.packages("kableExtra")

library(kableExtra)
library(tidyverse)
library(ggplot2)
library(opendatatoronto)
library(dplyr)
library(skimr)
```

```{r, echo=FALSE}
package <- show_package("7d72bbbe-8adc-4b36-8ad1-5359f1c7a9cc")

resources <- list_package_resources("7d72bbbe-8adc-4b36-8ad1-5359f1c7a9cc")

datastore_resources <- filter(resources, tolower(format) %in% c('csv', 'geojson'))

data <- filter(datastore_resources, row_number()==1) %>% get_resource()
```


# Introduction

This research looks at homicide cases in Toronto from 2004 to 2019. The dataset was taken from Open Data Toronto. 

The main interests are on the type of homicide and the occurrence year. I expected that the cases of homicide would increase with time but the results show that the number did not really increase with time. 

Another interest was to find which area has the most cases but there are 134 unique areas in the data so it was difficult to represent the results in a graph. Furthermore, there are only 3 given homicide types, and one of them is 'other', so it is not clear what types are included in 'other'.

# Data

The Open Data Toronto Dataset is Homicide and the first six rows of it are shown below. 
```{r, message=FALSE, warning=FALSE}
kable(head(data)) %>%
  kable_styling(font_size = 7)
```
The main variables we focus on are Occurence_year and Homicide_Type. The 3 homicide types in this dataset are shooting, stabbing and other. The dates are from 2004 to 2019. 


```{r, message=FALSE, warning=FALSE}
skimr::skim(data)
```


# Graphs


```{r, echo=FALSE}
data %>%
  ggplot(aes(x = Occurrence_year)) +
  geom_bar() +
  labs(x = "Occurrence Year",
       y = "Number",
       title = "Occurence Year of Homicide in Toronto",
       caption = "Source: Toronto Police Services (2020)") +
  theme_light()
```
The graph is not skewed and is not very steady as well. There is no clear pattern so it would be hard to guess future number of cases as well. 

```{r, echo=FALSE}
data %>%
  ggplot(aes(x = Homicide_Type)) +
  geom_bar() +
  labs(x = "Homicide Type",
       y = "Number",
       title = "Distribution of Homicide Type in Toronto (2004-2019)",
       caption = "Source: Toronto Police Services (2020)") +
  theme_light()
```
It is clear that most cases of homicide are due to shooting. The second most is due to stabbing but it does not even occur half as much as shooting. 


# References

- Hadley Wickham, Jim Hester and Winston Chang (2020). devtools: Tools to Make Developing R Packages Easier. R
  package version 2.3.2. https://CRAN.R-project.org/package=devtools.
- Hadley Wickham, Romain François, Lionel Henry and Kirill Müller (2020). dplyr: A Grammar of Data
  Manipulation. R package version 1.0.0. https://CRAN.R-project.org/package=dplyr.
- Wickham et al., (2019). Welcome to the tidyverse. Journal of Open Source Software, 4(43), 1686,
  https://doi.org/10.21105/joss.01686.
- Toronto Police Services (2020). Homicide: This dataset includes all Homicides from 2004 to 2019. https://open.toronto.ca/dataset/homicide/.   
- JJ Allaire and Yihui Xie and Jonathan McPherson and Javier Luraschi and Kevin Ushey and Aron Atkins and Hadley Wickham and Joe Cheng and Winston Chang and Richard Iannone (2020). rmarkdown: Dynamic Documents for R. R package version 2.3. https://rmarkdown.rstudio.com.
- R Core Team (2020). R: A language and environment for statistical computing. R, Foundation for Statistical Computing, Vienna, Austria. https://www.R-project.org/.
- Hao Zhu (2020). kableExtra: Construct Complex Table
  with 'kable' and Pipe Syntax.
  http://haozhu233.github.io/kableExtra/,
  https://github.com/haozhu233/kableExtra.
- Elin Waring, Michael Quinn, Amelia McNamara, Eduardo
  Arino de la Rubia, Hao Zhu and Shannon Ellis (2020).
  skimr: Compact and Flexible Summaries of Data.
  https://docs.ropensci.org/skimr (website),
  https://github.com/ropensci/skimr.
